### 2018-07-16 paper/design.tex
fig
Removes no-longer-needed building-blocks.tex
Revert "Removes no-longer-needed building-blocks.tex"
This reverts commit 3df1ce56ed39870f643f26e4addb2865992f00ab.
Revert "Revert "Removes no-longer-needed building-blocks.tex""
This reverts commit 0e7094c6269f84c38fd505739131958cc5b14360.
comments with placeholders for intentions

\section{Design of the \name file exchange system}
\label{design}
This section presents the \name protocol in detail.
Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file $f$ through \name; they start by sharing some information out-of-band, e.g. from their smartphones.
More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.

@@

\begin{figure}[t]
\centering
\def\svgwidth{\columnwidth}
%\input{outline.pdf_tex}
\import{figures/}{outline.pdf_tex}
%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
\caption{\label{fig:outline}Outline of \name's components. Users squads of devices are circled in gray. From top to bottom: a user's devices collaborate through the Squad Overlay; online devices globally share information about them to random peers; using the two above overlays allows for the creation or Predictive Onion Routes (PORs) between sets of devices; secure file exchange between users is enabled by PORs.}
\end{figure}

@@

\include*{building-blocks}
\include*{squad-overlay-design}
\include*{global-overlay-design}
\include*{message-passing-design}
%\include*{file-exchange-design}

>>>>

\section{Design of the \name file exchange system}
\label{design}
\sonja{will frame and structure A) squad overlay (prediction) B)
  global overlay (RPS) C) sphinxes (incl. sphinx, onion routing in
  general) D) SPOR and SPORES E) encryption (hybrid, payload, header)
  if not included earlier F) out-of-band}
\sonja{remove/update references to building blocks, POR}

This section presents the \name protocol in detail.
Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file $f$ through \name; they start by sharing some information out-of-band, e.g. from their smartphones.
More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.

@@

\begin{figure}[t]
\centering
\def\svgwidth{0.8\columnwidth}
%\input{outline.pdf_tex}
\import{figures/}{outline.pdf_tex}
%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
\caption{\label{fig:outline}Outline of \name's components. Users squads of devices are circled in gray. From top to bottom: a user's devices collaborate through the Squad Overlay; online devices globally share information about them to random peers; using the two above overlays allows for the creation or Predictive Onion Routes (PORs) between sets of devices; secure file exchange between users is enabled by PORs.}
\end{figure}

@@

\include*{squad-overlay-design}
\include*{global-overlay-design}
\include*{sphinxes}
\include*{message-passing-design}
%\include*{file-exchange-design}
